Solving the maximum independant set problem by generic programming einsum networks

### 2021-06-16 paper/paper.tex
update

\centerline{\begin{tikzpicture}
    \def\r{0.1}
    \def\a{0.1}
    \foreach \x in {1,...,5}
        \foreach \y in {1,...,5}{
        \node[fill, regular polygon, 
            regular polygon sides=3, scale=0.3, rotate=90] at (\x+0.1, \y+0.2) {};
        \draw [black,thick] (\x,\y) -- (\x+0.1,\y+0.2);
        }
    \foreach \x in {1,...,5}
        \foreach \y in {1,...,4}{
            \filldraw[fill=black] (\x-\a,\y+0.5-\a) rectangle (\x+\a, \y+0.5+\a);
            \filldraw[fill=black] (\y+0.5-\a,\x-\a) rectangle (\y+0.5+\a, \x+\a);
            \draw [black,thick] (\x,\y) -- (\x,\y+1);
            \draw [black,thick] (\y,\x) -- (\y+1,\x);
        }
    \foreach \x in {1,...,4}
        \foreach \y in {1,...,4}{
            \filldraw[fill=black] (\x+0.3-\a,\y+0.3-\a) rectangle (\x+0.3+\a, \y+0.3+\a);
            \filldraw[fill=black] (\y+0.3-\a,\x+0.7-\a) rectangle (\y+0.3+\a, \x+0.7+\a);
            \draw [black,thick] (\x,\y) -- (\x+1,\y+1);
            \draw [black,thick] (\y+1,\x) -- (\y,\x+1);
        }
\end{tikzpicture}}

>>>>

\centerline{\begin{tikzpicture}
    \def\r{0.1}
    \def\a{0.07}
    \def\L{0.6}
    \def\l{0.1}
    \foreach \x in {1,...,5}
        \foreach \y in {1,...,5}{
        \node[fill, regular polygon, 
            regular polygon sides=3, scale=0.3] at (\x, \y) {};
        }
    \foreach \x in {1,...,5}
        \foreach \y in {1,...,5}{
            \ifnum \y < 5
                \filldraw[fill=black] (\x-\a,\y+0.5-\a) rectangle (\x+\a, \y+0.5+\a);
                \filldraw[fill=black] (\y+0.5-\a,\x-\a) rectangle (\y+0.5+\a, \x+\a);
            \fi
            \filldraw [red, opacity=0.3] plot [smooth cycle] coordinates {(\x-\L,\y+\l) (\x-\l,\y+\l) (\x-\l, \y+\L) (\x+\l,\y+\L) (\x+\l,\y+\l) (\x+\L,\y+\l) (\x+\L,\y-\l) (\x+\l,\y-\l) (\x+\l,\y-\L) (\x-\l,\y-\L) (\x-\l,\y-\l) (\x-\L,\y-\l)};
        }
    \foreach \x in {1,...,4}
        \foreach \y in {1,...,4}{
            \filldraw[fill=black] (\x+0.3-\a,\y+0.3-\a) rectangle (\x+0.3+\a, \y+0.3+\a);
            \filldraw[fill=black] (\y+0.3-\a,\x+0.7-\a) rectangle (\y+0.3+\a, \x+0.7+\a);
        }
\end{tikzpicture}}
